A weakly structured stem for human origins in Africa

### 2022-12-23 paper.tex
Geographic affiliation in Discussion
Update paper.tex

Our inferred models paint a consistent picture of the Middle to Late Pleistocene as a 
critical period of change, assuming that estimates from the recombination clock accurately relate to geological chronologies
(SI Section~\ref{sec:supp-mutation}). 
During the late Middle Pleistocene, the multiple merger model indicates three
major stem lineages in Africa, tentatively assigned to southern (Stem 1S),
eastern (Stem 1E) and western/central Africa (Stem 2). Geographic association was informed by 
the present population location with the greatest ancestry contribution from each stem. For example,
Stem 1S contributes 71% to the ancestral formation of the Khoe-San. The extent of the isolation >400ka
between Stem 1S and Stem 1E
suggests that these two stems were not proximate to each other. While the length of
isolation among the stems is variable across model fits, models with a period of 
divergence, isolation and then a merger event (i.e. a ``reticulation'')
out-performed models with bifurcating divergence and continuous gene flow.

>>>>

Our inferred models paint a consistent picture of the Middle to Late Pleistocene as a 
critical period of change, assuming that estimates from the recombination clock accurately relate to geological chronologies
(SI Section~\ref{sec:supp-mutation}). 
During the late Middle Pleistocene, the multiple merger model indicates three
major stem lineages in Africa, tentatively assigned to southern (Stem 1S),
eastern (Stem 1E) and western/central Africa (Stem 2). Geographic association was informed by 
the present population location with the greatest ancestry contribution from each stem. For example,
Stem 1S contributes 71\% to the ancestral formation of the Khoe-San. The extent of the isolation >400ka
between Stem 1S, Stem 1E and Stem 2 suggests that these stems were not proximate to each other. While the length of
isolation among the stems is variable across model fits, models with a period of 
divergence, isolation and then a merger event (i.e. a ``reticulation'')
out-performed models with bifurcating divergence and continuous gene flow.
